DATA 621 Homework #3

### 2019-10-31 hw3/HW3.Rmd
Update HW3

## Data Preparation

@@

### Example of the new meta feature
The first graph below is the difference between the distributions and the second graph is the new derived predictive feature
```{r}

density_diff(train,test,"age",train$target,"age_density")$dist
density_diff(train,test,"age",train$target,"age_density")$dist_diff
```

## Model Building

@@

Looking these three models together, `model1` looks like the best one. Although the full model scored an F1 that was ever-so-slightly higher on our test data set, `model1` has half the predictors and it's scores are almost exactly the same as `fullmodel`.

@@

>>>>

## Basic Model Building

## Alternative Models

@@

### Example of the new meta feature
The first graph below is the difference between the distributions and the second graph is the new derived predictive feature
```{r}
density_diff(train,test,"age",train$target,"age_density")$dist
density_diff(train,test,"age",train$target,"age_density")$dist_diff
```

With our new density variables, we can run another model:

@@

Looking the three models together, `model1` looks like the best one. Although the full model scored an F1 that was ever-so-slightly higher on our test data set, `model1` has half the predictors and it's scores are almost exactly the same as `fullmodel`.

@@

ROC curves can give us another look at which model might be better suited for prediction.
